Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-11-25 _tex/index.tex
Built site for gh-pages

{``However'' paragraph}

>>>>

But the psychometric and statistical literature strongly advises against
ignoring additional traits that could confound the measurement of the
trait of interest, overlooking clustering (grouping) structures, or
mis-specifying the trait's measurement model. First, when additional
traits are ignored in favor of a unidimensional trait structure, such as
when judges' biases are disregarded, the association between stimuli
does not vanish \citep[pp.~346]{vanderLinden_et_al_2017_II}. This
mismatch can result in a potential overestimation of precision
(reliability) in the measurement process
\citep[pp.~340-341]{Hoyle_et_al_2023}, or worse, introduce bias into the
trait's measurement \citep{Ackerman_1989}. Second, when relevant
hierarchical (or grouping) structures are present in the data, ignoring
these structures can further exacerbate the inflation of measurement
reliability (citation needed). Lastly, mis-specifying the measurement
model by assuming, for example, equal discriminal dispersions across
stimuli can overlook meaningful differences in the reliability of the
trait. Taken together, these mis-specifications and oversights can lead
to misleading conclusions about the trait measurement, ultimately
casting doubts about the validity of the trait, as validity cannot exist
without reliability \citep[pp.~2]{Perron_et_al_2015}.
